---
title: "Using the GermaParl Annotation"
author: "Andreas Blätte (andreas.blaette@uni-due.de)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GermaParl CAP Annotation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Loading packages

```{r load_polmineR.anno, eval = FALSE}
library(polmineR)
library(magrittr)
use("GermaParl")
```


## Inspect Annotations

First, we create a partition with a speech that has been annotated.

```{r, eval = FALSE}
P <- partition(
  "GERMAPARL",
  lp = 13, session = 104, speaker = "Amke Dietert-Scheuer",
  xml = "nested"
  )
if (interactive()) read(P)
```

Second, let us get the unique annotations that are present.

```{r, eval = FALSE}
annos <- strsplit(sAttributes(P, "cap"), split = "\\|") %>%
  unlist() %>% unique()
annos <- annos[-which(annos %in% "")]
annos
```

Third, skip through the annotations.

```{r, eval = FALSE}
for (anno in annos){
  message("annotation: ", anno)
  P2 <- partition(
    P, cap = sprintf("^.*%s.*$", anno), xml = "nested", regex = TRUE
    )
  cpos <- apply(P2@cpos, 1, function(x) x[1]:x[2]) %>% unlist() %>% unique()
  P %>% html() %>% highlight(list(yellow = cpos)) %>% show()
  if (readline(prompt = "print 'q' to exit, any other key to continue") == "q") break
}
```


# Use Annotations for a simply search engine

```{r load_packages2, eval = FALSE}
library(polmineR)
use("GermaParl")

library(qlcMatrix)
library(Matrix)

library(magrittr)
```

```{r create_partition, eval = FALSE}
cap_id <- "8-01" # Nuclear Energy
cap_regex <- sprintf("^.*\\|%s\\|.*$", cap_id)
P <- partition(
  "GERMAPARL", cap = cap_regex, regex = TRUE,
  pAttribute = "word"
  )
```


```{r create_ctm, eval = FALSE}
# dtm <- as.DocumentTermMatrix("GERMAPARL", pAttribute = "word", sAttribute = "speech") # 90-100 secs
# saveRDS(dtm, file = "~/Lab/tmp/dtm.RData")
dtm <- readRDS(file = "~/Lab/tmp/dtm.RData") # ~ 3 secs
```

We now fold in the counts for the annotation subcorpus into the document-term-matrix.

```{r fold_in_search_vector, eval = FALSE}
dtm$i <- c(dtm$i, rep(x = nrow(dtm) + 1, times = nrow(P))) %>% as.integer()
dtm$v <- c(dtm$v, P[["word"]]) %>% as.integer()
dtm$j <- c(dtm$j, P[["word_id"]]) %>% as.integer()
dtm$nrow <- as.integer(dtm$nrow + 1L)
dtm$dimnames[[1]] <- c(dtm$dimnames[[1]], "search_vector")
```

Remove short speeches, apply tf-idf weight, and generate input format the cosSparse function requires.

```{r some_cleaning, eval = FALSE}
dtm2 <- dtm[which(row_sums(dtm) >= 250),]
dtm3 <- weigh(dtm2, method = "tfidf")
M <- t(as.sparseMatrix(dtm3))
```

Now we compare the search vector (Y) with all the documents.

```{r get_cosine_similarities, eval = FALSE}
simMatrix <- cosSparse(
  X = M[, 1:(ncol(M) - 1)], 
  Y = Matrix(as.matrix(M[,ncol(M)]))
  )
```

Rank documents by similarity score ...

```{r similarity_vector, eval = FALSE}
simVector <- setNames(simMatrix[,1], rownames(simMatrix))
simVectorOrdered <- simVector[order(simVector, decreasing = TRUE)]
```

Get the terms with the highest tf-idf values to highlight them.

```{r query_vector, eval = FALSE}
query <- setNames(as.vector(dtm3["search_vector",]), colnames(dtm3))
query <- query[order(query, decreasing = TRUE)]
```

Skip through the speeches that match the search vector (generated from the annotations) best. 

```{r skip_query_results, eval = FALSE}
for (x in names(simVectorOrdered)[1:25]){
  print(x)
  partition("GERMAPARL", speech = x) %>%
    read() %>% 
    highlight(list(yellow = names(head(query, 250)))) %>%
    show()
  if (readline("'q' to quit, any other key to proceed") == "q") break
}
```
